Results

### 2024-09-13 scripts/Results.Rmd
leaf plot

linecols <- c( # define our palette
  'Species' = 'grey50',
  "Mean" = "#093824", 
  "95% CI" = "#73BA9B",
  "Populations" = "#FF2C55"
  )

ggplot(suitability_amounts,
       aes(x = Percent, y = Records, color = Species, group = Species)) +
  geom_line(lty = 1) +
  scale_color_grey(guide = 'none') + 
  geom_ribbon(data = suitability_means, aes(ymin = lower, ymax = upper, x = Percent),
              fill = '#73BA9B', inherit.aes = F, alpha = 0.5) + 
  geom_line(data = suitability_means, 
            aes(x = Percent, y =  mean, color = 'a'), 
            color = '#093824', inherit.aes = F, lwd = 1) + 
  geom_line(data = suitability_means, aes(y = Percent/100, x = Null_mod),
            color = '#d95f02', inherit.aes = F,  lwd = 1, lty = 53, linemitre = 2) +
  geom_line(data = fp, aes(y = suitability, x = obs*100),
            color = '#7570b3', inherit.aes = F,  lwd = 1, lty = 53) +

  labs(
    title = 'Populations are found in\nareas with higher suitability',
    x = "Raster Cells (cumulative)",
    y = 'Predicted Suitability') + 
  theme_classic() +
  scale_y_continuous(
    breaks = seq(0, 1, by = 0.2)
  )  +

  scale_x_continuous(
    breaks = seq(0, 100, by = 20), labels = \(x) paste0(x, "%"), 
          sec.axis = sec_axis(~., name = 'Populations Found (cumulative)', 
                        breaks = seq(0, 100, by = 20), labels = \(x) paste0(x, "%"))) + 
  theme(
    plot.title = element_text(hjust = 0.5),
    aspect.ratio = 1/1) +

@@

  geom_label(data = labs, aes(x = x, y = y, label = label), inherit.aes = F, size = 2.5)

# rm(fp, fp_2, fp_5, fp_8, labs, prctn, sm50, sm80, linecols)
```

>>>>

linecols <- c( # define our palette
  'Species' = 'grey50',
  "Mean (95% CI)" = "#093824", 
  "95% CI" = "#73BA9B",
  "Observed Populations" = "#7570b3",
  'Theoretical Probability' = '#d95f02'
  )

ggplot(suitability_amounts,
       aes(x = Percent, y = Records, color = Species, group = Species)) +
  geom_line(lty = 1) +
  scale_color_grey(guide = 'none') + 
  ggnewscale::new_scale_color() +
  geom_ribbon(data = suitability_means, aes(ymin = lower, ymax = upper, x = Percent, fill = '95% CI'),
              inherit.aes = F, alpha = 0.5) + 
  geom_line(data = suitability_means, 
            aes(x = Percent, y =  mean, color = 'Mean (95% CI)'), 
            inherit.aes = F, lwd = 1) + 
  geom_line(data = suitability_means, aes(y = Percent/100, x = Null_mod, color = 'Theoretical Probability'),
            inherit.aes = F, lwd = 1) +
  geom_line(data = fp, aes(y = suitability, x = obs*100, color = 'Observed Populations'), inherit.aes = F, lwd = 1) +

  labs(
    title = 'Populations are found in areas\nwith higher predicted suitability',
    x = "Raster Cells (cumulative)",
    y = 'Predicted Suitability') + 
  theme_classic() +
  scale_y_continuous(
    breaks = seq(0, 1, by = 0.2)
  )  +
  scale_fill_manual(values = linecols, guide = 'none') + 
  scale_colour_manual(values = linecols, name = NULL) +

  scale_x_continuous(
    breaks = seq(0, 100, by = 20), labels = \(x) paste0(x, "%"), 
          sec.axis = sec_axis(~., name = 'Populations Found (cumulative)', 
                        breaks = seq(0, 100, by = 20), labels = \(x) paste0(x, "%"))) + 
  theme(
    legend.position=c(.9,.10),
    plot.title = element_text(hjust = 0.5),
    aspect.ratio = 1/1) +

@@

  geom_label(data = labs, aes(x = x, y = y, label = label), 
             inherit.aes = F, size = 2.5,
             fill='transparent', color = 'white') +

  ######        USE THIS TO MAKE THE PLOT TRANSPARENT FOR THE TALK        #####

  theme(
    panel.background = element_rect(fill='transparent'), #transparent panel bg
    plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
    panel.grid.major = element_blank(), #remove major gridlines
    panel.grid.minor = element_blank(), #remove minor gridlines
    legend.background = element_rect(fill='transparent'), #transparent legend bg
    legend.box.background = element_rect(fill='transparent'), #transparent legend panel
    text = element_text(colour = "white")
  )

ggsave('../plots/leafplot-trans.png', width = 9, height = 9, units = 'in')

rm(fp, fp_2, fp_5, fp_8, labs, prctn, sm50, sm80, linecols)
```
